### 2024-03-15 sections/2homology.tex
ignore this for the moment

More generally, an \emph{$\infty$-operad}, after \cite{lurie_ha}, is a map $\mathscr{C}\to\mathsf{Fin}_\ast$ which is only required to be a cocartesian fibration upon restricting to $\mathsf{Fin}_{\ast}^{\text{inrt}}\subset\mathsf{Fin}_\ast$, the subcategory of \emph{inert} morphisms $f\colon\langle m\rangle\to \langle n\rangle$ for which, by definition, $f^{-1}\{i\}$ is a singleton whenever $i\in\langle n\rangle^{\circ}\coloneqq\{1,\dots,n\}\subset\langle n\rangle$.

>>>>

More generally, an \emph{$\infty$-operad} is a map $\catC\to\mathsf{Fin}_\ast$ that satisfies a generalisation of the properties of a symmetric monoidal $\infty$-category -- see \cite[Definition 2.1.1.10]{lurie_ha}.
